Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
CFG->NFA->DFA fig fixed

\begin{figure}[t!]
  \begin{tabular}{cc}
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(50,12)
  \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}}
  \putnode{t1}{t0}{15}{0}{\pscirclebox{\mbox{\ \ \ \ }}} \hspace{5mm}
  \putnode{t2}{t1}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->}
  \ncline{t0}{t1}
  \ncline{t1}{t2}
  \putnode{l0}{t1}{7}{2}{\clazy}
  \nccurve[angleA=45, angleB=135, ncurv=4, nodesep=-1]{t1}{t1}
  \putnode{l1}{t1}{0}{8}{\acdr, \clazy}
  \nccurve[angleA=45, angleB=135, ncurv=3, nodesep=-1]{t2}{t2}
  \putnode{l2}{t2}{0}{8}{\clazy}
\end{pspicture}
&
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(30,12)
  \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}}
  \putnode{t1}{t0}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->}
  \ncline{t0}{t1}
  \nccurve[angleA=45, angleB=135, ncurv=3, nodesep=-1]{t1}{t1}
  \putnode{l1}{t1}{0}{8}{\acdr}
\end{pspicture}
\\
(a) & (b) \\
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(50,12) %\psframe(0,-5)(40,12)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{9}{\pa}}}
  \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \ }}} \hspace{5mm}
  \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{\ \ \ \ }}}
%  \putnode{t3}{t2}{12}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->}
  \ncline{t0}{t1}
  \ncline{t1}{t2}
  \putnode{l0}{t1}{5}{2}{\clazy}
%  \ncline{t2}{t3}
%  \nccurve[angleA=55, angleB=125, ncurv=3, nodesep=-.8]{t3}{t3}
%  \putnode{l2}{tD1}{0}{10}{\acdr}
 \putnode{tD1}{t2}{12}{0}{\pscirclebox{\mbox{\ \ \ \ }}} \hspace{5mm}
  \putnode{tD2}{tD1}{12}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->}
  \ncline{t2}{tD1}
  \putnode{l1}{t2}{5}{2}{\bcar}
  \ncline{tD1}{tD2}
  \putnode{lD0}{tD1}{5}{2}{\clazy}
  \nccurve[angleA=45, angleB=135, ncurv=4, nodesep=-1]{tD1}{tD1}
  \putnode{lD1}{tD1}{0}{8}{\acdr, \clazy}
  \nccurve[angleA=45, angleB=135, ncurv=3, nodesep=-1]{tD2}{tD2}
  \putnode{lD2}{tD2}{0}{8}{\clazy}
\end{pspicture}
&
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(20,12) %\psframe(0,-5)(40,12)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{9}{\pa}}}
  \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \ }}} \hspace{5mm}
  \psset{arrows=->}
  \ncline{t0}{t1}
\end{pspicture}
\\
(c) & (d)  \end{tabular}
\caption{(a) The  grammar rules for \var{\Df{\length}{1}}
  converted into an automaton, and simplified in (b). The same for \var{\Lanv{9}{\pa}}
  is shown in (c) and (d)}\label{fig:example-automata}
\figrule
\end{figure}

>>>>

\begin{figure}[t!]
  \begin{tabular}{cc}
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(50,12)
  \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}}
  \putnode{t1}{t0}{15}{0}{\pscirclebox{\mbox{\ \ \ \ }}} \hspace{5mm}
  \putnode{t2}{t1}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->}
  \ncline{t0}{t1}
  \ncline{t1}{t2}
  \putnode{l0}{t1}{7}{2}{\clazy}
  \nccurve[angleA=45, angleB=135, ncurv=4, nodesep=-1]{t1}{t1}
  \putnode{l1}{t1}{0}{8}{\acdr, \clazy}
  \nccurve[angleA=45, angleB=135, ncurv=3, nodesep=-1]{t2}{t2}
  \putnode{l2}{t2}{0}{8}{\clazy}
\end{pspicture}
&
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(30,12)
  \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}}
  \putnode{t1}{t0}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->}
  \ncline{t0}{t1}
  \nccurve[angleA=45, angleB=135, ncurv=3, nodesep=-1]{t1}{t1}
  \putnode{l1}{t1}{0}{8}{\acdr}
\end{pspicture}
\\
(a) & (b) \\
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(50,12) %\psframe(0,-5)(40,12)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{9}{\pa}}}
  \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \ }}} \hspace{5mm}
  \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{\ \ \ \ }}}
%  \putnode{t3}{t2}{12}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->}
  \ncline{t0}{t1}
  \ncline{t1}{t2}
  \putnode{l0}{t1}{5}{2}{\clazy}
%  \ncline{t2}{t3}
%  \nccurve[angleA=55, angleB=125, ncurv=3, nodesep=-.8]{t3}{t3}
%  \putnode{l2}{tD1}{0}{10}{\acdr}
 \putnode{tD1}{t2}{12}{0}{\pscirclebox{\mbox{\ \ \ \ }}} \hspace{5mm}
  \putnode{tD2}{tD1}{12}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->}
  \ncline{t2}{tD1}
  \putnode{l1}{t2}{5}{2}{\bcar}
  \ncline{tD1}{tD2}
  \putnode{lD0}{tD1}{5}{2}{\clazy}
  \nccurve[angleA=45, angleB=135, ncurv=4, nodesep=-1]{tD1}{tD1}
  \putnode{lD1}{tD1}{0}{8}{\acdr, \clazy}
  \nccurve[angleA=45, angleB=135, ncurv=3, nodesep=-1]{tD2}{tD2}
  \putnode{lD2}{tD2}{0}{8}{\clazy}
\end{pspicture}
&
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(20,12) %\psframe(0,-5)(40,12)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{9}{\pa}}}
  \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \ }}} \hspace{5mm}
  \psset{arrows=->}
  \ncline{t0}{t1}
\end{pspicture}
\\
(c) & (d)  \end{tabular}
\caption{(a) The  grammar rules for \var{\Df{\length}{1}}
  converted into an automaton, and (b) its DFA. The same for \var{\Lanv{9}{\pa}}
  are shown in (c) and (d)}\label{fig:example-automata}
\figrule
\end{figure}
